Solving a probabilistic planning problem by presenting a history in the field of probabilistic planning

### 2014-04-13 FinalPaper/paper.tex
Comment todos and worries

\begin{enumerate}
	\item Start trial at $s_0$
	\item Take action based on current value function $V$ (similar to reward) \myworries{moeten we bellman backup of value function nog uitleggen}
	\item Perform Bellman backup
	\item Sample the outcome and update $V$
	\item Transition to the next state
	\item Repeat step 2 - 5 until a goal, dead end or converged state is reached
	\item Check if all states have converged, otherwise start a new trial (step 2 - 6)
\end{enumerate}

@@

\subsection{Domain Evaluation}
\myworries{hier alleen een evalutie geven, niet wederom een uitleg, anders moet je het hierboven uitleggen. Alles wat je zegt, moet een reden hebben, anders kan het weg}

@@

\todo{connect back to the purpose of the paper}

@@

To choose an appropriate planner for our UAV domain, we have analyzed some of
the most important domains in the course of history of probabilistic planners.
The UAV domain seems to have resemblances of the \textsc{Navigation} domain
and the \textsc{SysAdmin} domain. With this knowledge a proposal can be made
for a matching planner.

@@

\todo{we hadden hier al meer voor klaar staan dan alleen dit toch? Het is nog niet echt een aanbeveling}

>>>>

\begin{enumerate}
	\item Start trial at $s_0$
	\item Take action based on current value function $V$ (similar to reward)
%\myworries{moeten we bellman backup of value function nog uitleggen}
	\item Perform Bellman backup
	\item Sample the outcome and update $V$
	\item Transition to the next state
	\item Repeat step 2 - 5 until a goal, dead end or converged state is reached
	\item Check if all states have converged, otherwise start a new trial (step 2 - 6)
\end{enumerate}

@@

\subsection{Domain Evaluation}
%\myworries{hier alleen een evalutie geven, niet wederom een uitleg, anders moet je het hierboven uitleggen. Alles wat je zegt, moet een reden hebben, anders kan het weg}

@@

%\todo{connect back to the purpose of the paper}

@@

To choose an appropriate planner for our UAV domain, we have analyzed some of
the most important domains in the course of history of probabilistic planners.
The UAV domain seems to have resemblances to the \textsc{Navigation} domain
and the \textsc{SysAdmin} domain. With this knowledge a proposal can be made
for a matching planner.

@@

%\todo{we hadden hier al meer voor klaar staan dan alleen dit toch? Het is nog niet echt een aanbeveling}
